# Build DuckDB

This notebook builds the DuckDB database & base tables from scratch. Everything not in this file is built via the scrapes later in the pipeline.

## Initialize

These are the core packages needed to build the database.

```{r}
library(DBI)
library(duckdb)
library(tidyverse)
library(zipcodeR)
library(jsonlite)
```

I'm using [DuckDB](https://duckdb.org/) for this project because flat files are annoying and DuckDB is light-weight and very easy to use.

```{r}
#| label: db-connect

con = dbConnect(duckdb(), "duck.db")
```

## Zip Codes

A lot of the addresses from the scrapes are non-standard, so this table of zip codes will help standardize the results. [zipcodeR]() makes it very easy to obtain tibbles of zip codes and relevant information, but it does use `<glob>` storage of `<raw>` values which was new for me. Shout out to [this](https://stackoverflow.com/a/77285606/26439015) Stack Overflow answer for suggesting the `jsonlite::parse_gzjson_raw()` solution.

```{r}
zip_codes = search_state("WV") |> 
  select(zipcode, major_city, cities = common_city_list, county) |>
  mutate(cities = map(cities, parse_gzjson_raw)) |> 
  unnest_longer(cities) |> 
  summarize(
    .by = c(zipcode, major_city, county), 
    cities = str_c(cities, collapse = "|"))

dbWriteTable(con, "zip_codes", zip_codes)
```

## Travel Regions

The WV Tourism website designated 9 different regions to the counties of WV as Travel Regions. I hate to admit it, but as these aren't **official** in anyway, I just had to make this table by hand.

```{r}
travel_region_county_cross = tribble(
  ~region,                         ~county,
  "Eastern Panhandle",             "Berkeley County",
  "Eastern Panhandle",             "Jefferson County",
  "Eastern Panhandle",             "Morgan County",
  "Hatfield-McCoy Mountains",      "Boone County",
  "Hatfield-McCoy Mountains",      "Lincoln County",
  "Hatfield-McCoy Mountains",      "Logan County",
  "Hatfield-McCoy Mountains",      "McDowell County",
  "Hatfield-McCoy Mountains",      "Mercer County",
  "Hatfield-McCoy Mountains",      "Mingo County",
  "Hatfield-McCoy Mountains",      "Wayne County",
  "Hatfield-McCoy Mountains",      "Wyoming County",
  "Metro Valley",                  "Cabell County",
  "Metro Valley",                  "Kanawha County",
  "Metro Valley",                  "Mason County",
  "Metro Valley",                  "Putnam County",
  "Mid-Ohio Valley",               "Calhoun County",
  "Mid-Ohio Valley",               "Jackson County",
  "Mid-Ohio Valley",               "Pleasants County",
  "Mid-Ohio Valley",               "Ritchie County",
  "Mid-Ohio Valley",               "Roane County",
  "Mid-Ohio Valley",               "Wirt County",
  "Mid-Ohio Valley",               "Wood County",
  "Mountain Lakes",                "Braxton County",
  "Mountain Lakes",                "Clay County",
  "Mountain Lakes",                "Gilmer County",
  "Mountain Lakes",                "Lewis County",
  "Mountain Lakes",                "Nicholas County",
  "Mountain Lakes",                "Upshur County",
  "Mountain Lakes",                "Webster County",
  "Mountaineer Country",           "Barbour County",
  "Mountaineer Country",           "Doddridge County",
  "Mountaineer Country",           "Harrison County",
  "Mountaineer Country",           "Marion County",
  "Mountaineer Country",           "Monongalia County",
  "Mountaineer Country",           "Preston County",
  "Mountaineer Country",           "Taylor County",
  "New River - Greenbrier Valley", "Fayette County",
  "New River - Greenbrier Valley", "Greenbrier County",
  "New River - Greenbrier Valley", "Monroe County",
  "New River - Greenbrier Valley", "Raleigh County",
  "New River - Greenbrier Valley", "Summers County",
  "Northern Panhandle",            "Brooke County",
  "Northern Panhandle",            "Hancock County",
  "Northern Panhandle",            "Marshall County",
  "Northern Panhandle",            "Ohio County",
  "Northern Panhandle",            "Tyler County",
  "Northern Panhandle",            "Wetzel County",
  "Potomac Highlands",             "Grant County",
  "Potomac Highlands",             "Hampshire County",
  "Potomac Highlands",             "Hardy County",
  "Potomac Highlands",             "Mineral County",
  "Potomac Highlands",             "Pendleton County",
  "Potomac Highlands",             "Pocahontas County",
  "Potomac Highlands",             "Randolph County",
  "Potomac Highlands",             "Tucker County"
)

dbWriteTable(con, "travel_region_county_cross", travel_region_county_cross)
```

## Finalize

Finally, we disconnect from the DB.

```{r}
dbListTables(con) |> as_tibble_col("tables")
dbDisconnect(con)
```
